A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-17 paper/paper.tex
Wee changes to comparison section
Typo. I'm sure it was James who did it.

Small scale experiments (not presented here) were performed to identify
suitable heuristics for selecting a label class abd a vertex within a label
class selection. Our heuristic of choice selects the label class with the
smallest $\min(|\setG|,|\setH|)$. From this class, a vertex is selected from
$\setG$ with maximum degree if $\graphH$ is sparse and with minimum degree if
$\graphH$ is dense. We discuss this further in \cref{sec:comparison}.

@@

In the CP-FC algorithm, each vertex $v \in \V(\graphG)$ is represented by a
variable, whose domain corresponds to the set of vertices in $\V(\graphH)$ to
which $v$ may currently be mapped, with an additional special $\bot$ value
representing an unmapped vertex.  Given a label class $\langle \setG,\setH
\rangle$ in \McSplit\, the vertices in $\setG$ correspond to variables in
CP-FC, and the vertices in $\setH$ to domain values. The label-class
representation of domains is possible because throughout the CP-FC algorithm
for maximum common subgraph, the domains of any two variables are either
identical or disjoint (excluding $\bot$, which is slightly more complicated).
To the best of our knowledge, this observation has not been made previously,
and it is not exploited in other implementations.

>>>>

Small scale experiments (not presented here) were performed to identify
suitable heuristics for selecting a label class and a vertex within a label
class selection. Our heuristic of choice selects the label class with the
smallest $\min(|\setG|,|\setH|)$. From this class, a vertex is selected from
$\setG$ with maximum degree if $\graphH$ is sparse and with minimum degree if
$\graphH$ is dense. We discuss this further in \cref{sec:comparison}.

@@

In the CP-FC algorithm, each vertex $v \in \V(\graphG)$ is represented by a
variable, whose domain corresponds to the set of vertices in $\V(\graphH)$ to
which $v$ may currently be mapped, with an additional special $\bot$ value
representing an unmapped vertex.  Given a label class $\langle \setG,\setH
\rangle$ in \McSplit\, the vertices in $\setG$ correspond to variables in
CP-FC, and the vertices in $\setH$ to domain values. The label-class
representation of domains is possible because throughout the CP-FC algorithm
for maximum common subgraph, the domains of any two variables are either
identical or disjoint (excluding $\bot$, which is either present in all domains or in none).
To the best of our knowledge, this observation has not been made previously,
and it is not exploited in other algorithms for maximum common subgraph.
